Computing volume via non-linear rectangular prisms

### 2019-07-31 Cav2D/article-template.tex
added some text to reson for needing vector calculus
improved vector notation

>>>>

As will become apparent later on in the article extending the definition of the Cavalieri integral as it appears in ?? into $\mathbb{R}^3$ is problematic. However,
if the definition in ?? is first re-expressed in vector calculus notation then it becomes trivial to extend it into $\mathbb{R}^3$.

Let $\mathbf{c}(t) = \left <c_x(t),c_y(t) \right>$ be the vector equation of $a(y)-a$. Note that, for every coordinate $(x_i^1,x_i^2) \in [a,b]  [a',b']$ there exists a unique $t\in\mathbb{R}$ such that
\begin{equation}
\label{eq:pat_rel}
\left <x_i^2,f(x_i^2) \right > = \left <x_i^1,0 \right> + \left<c_x(t),c_y(t) \right > 
\end{equation}
Equation~\eqref{eq:pat_rel} can be rewritten as
\begin{equation}
\label{eq:t_func}
c_y(t) = f(x_i^1 + c_x(t)).
\end{equation}
Equation~\eqref{eq:t_func} implies that $t$ can be expressed in terms of $x_i^1$. We can, therefore, calculate $h(x_i^1)$ using $t(x_i^1)$ via:
\begin{equation}
\label{eq:h_func}
x_i^2 = h(x_i^1) = x_i^1 + c_x\circ t(x_i^1).
\end{equation}
Equation~\eqref{eq:h_func} is a trivial consequence of the definition of $h$ and Equation~\eqref{eq:pat_rel}.

and as such $t(x_i^1)$ can be used to determine $h(x_i^1)$.
i.e. $t$ is a function

It is therefore possible to define $t$ in terms of $x_i^1$.
